\documentclass[margin,]{res}
\usepackage{enumitem}
         
\begin{document}
\moveleft.5\hoffset\centerline{\LARGE \bf Michael Sanderson}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
\moveleft.5\hoffset\centerline{(940) 783-2400 $\cdot$ michael@mtsanderson.com}
 
\begin{resume}
\section{SKILLS}
\begin{itemize}[leftmargin=10pt]
    \item \textit{Languages}: Python, Go, Haskell, Shell, SQL
    \item \textit{Protocols}: HTTP, DNS, TCP, UDP, LDAP
    \item \textit{Platforms}: Debian, Red Hat, Cloud Foundry, Heroku, VMWare
    \item \textit{Software}: FastAPI, Flask, Nginx, Gitlab, HAProxy, MySQL, Postgres, Oracle, Redis
    \item \textit{Concepts}: HTTP APIs, Release Engineering, Version Control, CI/CD, Configuration Management
\end{itemize}
\section{EXPERIENCE} 
    \textbf{Senior Software Engineer}
    \textit{University of North Texas System} \hfill 2019--present \\ [5pt]
    \begin{itemize}[leftmargin=10pt]
        \item \textit{ETL Using Python}: extract data from databases and web-based APIs, apply in-memory transformations, and load into 3rd party systems as required. A key example is the data synchronization process between the ERP and the Learning Management System.
        \item \textit{University Data API}: uses modern Python to build a REST API abstraction layer on top of an existing ERP system.
        \item \textit{Platform as a Service}: deployed an on-premise installation of the open-source project, Cloud Foundry. Abstracts away the underlying compute, storage, and networking details and allows developers to focus on their code. Prior to this platform, a developer could potentially wait days for infrastructure resources to be provisoned. Now, they can deploy in seconds.
        \item \textit{Mentorship}: provide individual training sessions to help skill-up team members in the use of Python, Linux, and Cloud Foundry.
    \end{itemize}
    \textbf{Systems Administrator Lead}
    \textit{University of North Texas System} \hfill 2015--2019 \\ [5pt]
    \begin{itemize}[leftmargin=10pt]
        \item Led a team of five Systems Administrators who were responsible for some of the University's most important applications such as the Learning Management and Degree Audit Systems.
        \item Spearheaded efforts to bring automation, infrastructure as code, source control, and application performance and availability monitoring to the team.
        \item Introduced tools such as Jenkins, Saltstack, GitLab, and Zabbix which are still in use today.
        \item Established a daily stand-up meeting to review work in progress on a Kanban board.
    \end{itemize}
    \textbf{Systems Administrator}
    \textit{University of North Texas System} \hfill 2011--2015 \\ [5pt]
    \begin{itemize}[leftmargin=10pt]
        \item Participated in an on-call rotation, and acted as the primary administrator for enterprise data reporting and analytics applications such as Cognos and Informatica.
        \item Utilized a Nagios monitoring server to provide performance and availability monitoring.
        \item Wrote automation scripts in Python to streamline routine tasks such as software installs, server reboots, etc.
    \end{itemize}
    \textbf{IT Service Technician I-III}
    \textit{University of North Texas} \hfill 2008-2011 \\ [5pt]
    \begin{itemize}[leftmargin=10pt]
        \item Acted as a member of helpdesk staff and provided 1st tier troubleshooting for common IT/Desktop Computer issues. Built strong troubleshooting skills, and learned to have patience while dealing with frustrated Faculty/Staff.
        \item Trained under a full-time member of staff to develop a Windows Desktop Deployment process using Microsoft SCCM.
    \end{itemize}
\section{EDUCATION} 
    \textbf{Bachelor of Science}
    \textit{University of North Texas, Denton, TX} \hfill 2015 \\ [5pt]
\end{resume}
\end{document}
